3.9: Logarithmic Regression

### 2019-11-22 static/slides/21-slides.Rmd
Add more F-tests to slides 21

- $F$ has two sets of degrees of freedom, $q$ for the numerator, $n-k-1$ for the denominator
]

@@

- Command is `linearHypothesis()`, comes from the `car` package

@@

# test that northcen=west=south=0
# # the first argument is the name of my regression ("unrestricted_reg")
linearHypothesis(unrestricted_reg, c("northcen", "west", "south")) 
```

@@

.font50[
```{r, echo=F}
summary(unrestricted_reg)
```
]

@@

@@

- "**statistic**" is the All F-test, "**p.value**" next to it is the p value from the F test!

>>>>

- $F$ has two sets of degrees of freedom:
  - $q$ for the numerator
  - $(n-k-1)$ for the denominator
]

@@

$$\widehat{Wage_i}=\hat{\beta_0}+\hat{\beta_1}Female_i+\hat{\beta_2}Northeast_i+\hat{\beta_3}Northcen+\hat{\beta_4}South_i$$

$$\widehat{Wage_i}=\hat{\beta_0}+\hat{\beta_1}Female_i$$

- $H_0: \beta_2 = \beta_3 = \beta_4 =0$

- $q = 3$ restrictions (F numerator df)

- $n-k-1 = 526-4-1=521$ (F denominator df)

# F-test Example III

- We can use the `car` package's `linearHypothesis()` command to run an $F$-test:
  - first argument: name of the (unrestricted) regression
  - second argument: vector of variable names (in quotes) you are testing

@@

# F-test
linearHypothesis(unrestricted_reg, c("northcen", "west", "south")) 
```

# Second F-test Example: Are Two Coefficients Equal?

- The second type of test is whether two coefficients equal one another

.content-box-green[
.green[**Example**]:

$$\widehat{wage_i}=\beta_0+\beta_1 \text{Adolescent height}_i + \beta_2 \text{Adult height}_i + \beta_3 \text{Male}_i$$

- Does height as an adolescent have the same effect on wages as height as an adult?

$$H_0: \beta_1=\beta_2$$

- What is the restricted regression?

$$\widehat{wage_i}=\beta_0+\beta_1(\text{Adolescent height}_i + \text{Adult height}_i )+ \beta_3 \text{Male}_i$$

- $q=1$ restriction

# Second F-test Example: Data

```{r, echo=T}
# load in data
heightwages<-read_csv("../data/heightwages.csv")

# make a "heights" variable as the sum of adolescent (height81) and adult (height85) height

heightwages <- heightwages %>%
  mutate(heights=height81+height85)

height_reg<-lm(wage96~height81+height85+male, data=heightwages)
height_restricted_reg<-lm(wage96~heights+male, data=heightwages)

```

# Second F-test Example: Data

- For second argument, set two variables equal, in quotes

```{r, echo=T}
linearHypothesis(height_reg, "height81=height85") # F-test 
```

- Insufficient evidence to reject $H_0$!

- The effect of adolescent and adult height on wages is the same

@@

```{css, echo = FALSE}
.smallcode .remark-code { /*Change made here*/
  font-size: 65% !important;
}
```

.smallcode[
```{r, echo=T}
summary(unrestricted_reg)
```
]
]

- Last line of regression output from `summary()` of an `lm()` object is an **All F-test**
  - $H_0:$ all $\beta's=0$ 
    - the regression explains no variation in $Y$
  - Calculates an `F-statistic` that, if high enough, is significant (`p-value` $<0.05)$ enough to reject $H_0$
]

@@

- Alternatively, if you use `broom` instead of `summary()` of `lm` object:
  - `glance()` command makes table of regression summary statistics
  - `tidy()` only shows coefficients

@@

- "**statistic**" is the All F-test, "**p.value**" next to it is the p value from the F test
